---
title: "R Markdown in Action"
author: "Rob Willhoft"
date: "6/11/2019"
output: html_document
---

```{r setup, include=FALSE}
# Load results from the analysis
# Errors and messages will not be printed because include is set to FALSE
source( "analysis.R" )

# Also load additional libraries that may be needed for output
library("knitr")
```

## Overview
This is a brief report regarding life expectancy for each country from 
1960 to 2015 ([source](https://data.worldbank.org/indicator/SP.DYN.LE00.IN)).
The data reveials that the 
country with the longest life expectancy was `r longest_le$Country.Name`, 
with a life expectancy of `r longest_le$expectancy`.
The expectancy was `r le_difference` years longer than 
the life expectancy in `r shortest_le$Country.Name`.

Here are the countries whose libe expectancy **improved the most** since 1960.

```{r top_10_gain, echo = FALSE}
# Show the top 10 table (specifying the column names to display)
kable( top_10_gain, col.names = c("Country", "Change in Life Expectancy"))
```

## Life Expectancy in 2015
To identify geographic variations in live expectancy, here is a choropleth map
of life expectancy in 2015:

```{r le_map, echo = FALSE}
mapCountryData(
  mapped_data,
  mapTitle = "Life Expectancy in 2015",
  nameColumnToPlot = "X2015",
  addLegend = FALSE,
  colourPalette = brewer.pal(7, "Blues")
)
```