---
title: "Chapter 18 - Dynamic Reports with R Markdown"
author: "Rob Willhoft"
date: "6/7/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 18.2 - Integrating Markdown and **R** code

### 18.2.1 - **R** Code Chunks

Write normal **markdown** out her, then create a code block:

```{r}
# Execute R code in here
course_number <- 201
```

Back to writing _markdown_ out here.

```{r options_example, echo = FALSE, message = TRUE}
# A code chunk named "options_example", with argument 'echo' assigned FALSE
# and argument 'message' assigned TRUE
course_number
course_number <- course_number + 100
course_number
```

### 18.2.2 - Inline Code

For example:

To calculate `3 + 4` insdie some text, you can use `` `3 + 4`  `` right in the _middle_.
When you knit this text, `` `3 + 4`  `` would be replaced with the number `r 3 + 4`.

So `course_number` has the value `r course_number`.

## 18.3 - Rendering Data and Visualizations in Reports

### 18.3.1 - Rendering Strings
```{r raw_print_example, echo = FALSE}
print("Hello world")
```

```{r stored_print_example, echo = FALSE}
msg <- "**Hello world**"
```

Below is the message to see:

`r msg`

### 18.3.2 - Rendering Markdown Lists

A list containing Markdown:

```{r list_example, echo = FALSE}
markdown_list <- "
- Lions
- Tigers
- Bears
- Oh my!
"
```

`r markdown_list`

```{r pasted_list_example, echo = FALSE}
animals <- c("Lions", "Tigers", "Bears", "Oh my!")
markdown_list <- paste( "-", animals, collapse = "\n" )
```

Here's the list:

`r animals`

And the Markdown list:

`r markdown_list`

### 18.3.3 - Rendering Tables

```{r kable_example, echo = FALSE }
library("knitr")

letters <- c("a", "b", "c", "d")
numbers <- 1:4
df = data.frame( letters = letters, numbers = numbers )
```

Without **kable**:

```{r df_print, echo = FALSE}
df
```

With **kable**:

```{r df_kable, echo = FALSE}
kable( df )
```

### 18.3.4 - Rendering Plots

```{r plot_example, echo = FALSE}
library( "ggplot2" )

ggplot( data = midwest ) +
  geom_point(
    mapping = aes( x = percollege, y = percadultpoverty, color = state )
  ) +
  scale_color_brewer( palette = "Set3" )
```

  )